Insect venom anaphylaxis: a case - control study of the European Anaphylaxis Registry

### 2019-07-04 analysis/paper/paper.Rmd
VAS analysis from the NORA conference
figures corrected

```{r adrenuse, fig.cap="**Therapy of IVA cases.** A: General managment methods in IVA and non-IVA. B: Reasons for not administering adrenaline in both IVA and non-IVA cases. C,D,E: Age, sex and severity distribution was matched in cases in both groups to allow for comparable results between IVA and non_IVA cases"}
fig_adrenuse1
```

@@

<!-- The following line inserts a page break when the output is MS Word. For page breaks in PDF, use \newpage on its own line.  -->
##### pagebreak

@@

##### pagebreak

@@

```{r flow,fig.width=6,fig.height=4}
knitr::include_graphics("../figures/flow.png")
```

##### pagebreak

@@

##### pagebreak

```{R adrenalineuse, fig.cap = "The proportion of insect venom elicited anaphylaxis cases that were treated with adrenaline in comparison to other elicitors.",fig.height=4,fig.width = 6}
fig_adrenuse1
```

##### pagebreak

```{r figsymptoms, fig.cap="Symptoms of insect venom anaphylaxis (IVA) compared to other elicitors",fig.width=9.5,fig.height = 6}
fig_symptoms
```

##### pagebreak

```{r figcofactors, fig.cap="Cofactors of insect venom anaphylaxis ad their relationship to severity of a reaction",fig.width=4.2,fig.height = 6}
cof_fig
```

>>>>

```{r adrenuse, fig.cap="**Therapy of IVA cases.** A: General managment methods in IVA and non-IVA. B: Reasons for not administering adrenaline in both IVA and non-IVA cases. C,D,E: "}
#fig_adrenuse1
```

@@

<!-- The following line inserts a page break when the output is MS Word. For page breaks in PDF, use \newpage on its own line.  -->
#####

@@

#####

@@

```{r flow,fig.width=6,fig.height=6, fig.cap=" A) Flow-diagram illustrating the rationale to include cases in our analysis. B,C,D: Sex, age, and severity distribution was matched in cases in both groups to allow for comparable results between IVA and non_IVA cases"}
ggarrange(ggplot()+
            background_image(png::readPNG("../figures/flow.png")),
          lower_panel,
          ncol = 1,
          nrow = 2,
          heights = c(1,0.4),
          labels = c("A","")
)
```

#####

@@

#####

```{r figsymptoms, fig.cap="Symptoms of insect venom anaphylaxis (IVA) compared to other elicitors",fig.width=9.5,fig.height = 8}
fig_symptoms
```

#####

```{r adrenalineuse, fig.cap = "Therapy modes in patients with IVA compared to oter elicitors. A)  B)",fig.height=10,fig.width = 7}

ggpubr::ggarrange(
  ggarrange(
    plotManagement,
    rf_ggplot_treatment,
    labels = c("A","B")
  ),
  #lower_panel,
  matrix_venom$p+
    labs (x = "", y = "")+
    geom_segment(aes(x = c(8.5),
                     xend = c(8.5), 
                     y = c(0.5),
                     yend = c(39.5)),color = "red")+
    geom_segment(aes(x = c(0.5),
                     xend = c(21.5), 
                     y = c(28.5),
                     yend = c(28.5)), color = "red" ),
  nrow = 2,
  heights = c(1.5,3),
  labels = c("","C")
)
```

#####

```{r figcofactors, fig.cap="Cofactors of insect venom anaphylaxis ad their relationship to severity of a reaction",fig.width=5,fig.height = 8}
cof_fig
```

# Supplementrary Figures

```{r treatmentmatrixother}
#matrix_other
```
